---
title: "Homework 1"
output: github_document
---

I'm an R Markdown document!

```{r setup}
library(tidyverse)
```

# Problem 1

Here's a **code chunk** that samples from 
a _normal distribution_ with a random sample size of 10, a logical vector indicating whether elements of the sample are greater than 0, a character vector of length 10,a factor vector of length 10, with 3 different factor “levels”:

```{r}
problem1_df = tibble(
  x = rnorm(10),
  vec_log = x > 0,
  vec_char = c("these","new","characters","are", "for", "homework","one","of", "data","science"),
  vec_factor = factor(c("single","divorced","married","married","single","divorced","divorced","single","divorced","married")),
)
```

### Subsection 2: Trying to take the mean of each variable 
```{r}
problem1_df
mean(pull(problem1_df,x))
mean(pull(problem1_df,vec_log))
mean(pull(problem1_df,vec_char))
mean(pull(problem1_df,vec_factor))
```

The mean of numbers and logical vectors is possible, however we can't take the mean of characters or factors. 

### Subsection 3: Convert variable to numeric
```{r}
as.numeric(pull(problem1_df,vec_log))
as.numeric(pull(problem1_df,vec_char))
as.numeric(pull(problem1_df,vec_factor))
```

We are unable to convert a character into a numeric, however we are able to convert a logic and factor into numeric.

# Problem 2

Here's a **code chunk** that load the penguins dataset, and finds the mean of the flipper length. 
```{r}
data("penguins", package = "palmerpenguins")
flipper_mean = mean(pull(penguins,flipper_length_mm), na.rm = TRUE)
```

The data in this dataset includes `r colnames(penguins)`. The size of dataset we have is `r nrow(penguins) * ncol(penguins)`. The mean flipper length is `r flipper_mean`.

### Subsection 2: Graphing of flipper length and bill length
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
