---
title: "Homework 1"
output: github_document
---

I'm an R Markdown document!

```{r setup}
library(tidyverse)
```

# Problem 1

Here's a **code chunk** that samples from 
a _normal distribution_ with a random sample size of 10, a logical vector indicating whether elements of the sample are greater than 0, a character vector of length 10,a factor vector of length 10, with 3 different factor “levels”:

```{r}
problem1_df = tibble(
  x = rnorm(10),
  vec_log = x > 0,
  vec_char = c("these","new","characters","are", "for", "homework","one","of", "data","science"),
  vec_factor = factor(c("single","divorced","married","married","single","divorced","divorced","single","divorced","married")),
)
```

### Subsection 2: Trying to take the mean of each variable 
```{r}
problem1_df
mean(pull(problem1_df,x))
mean(pull(problem1_df,vec_log))
mean(pull(problem1_df,vec_char))
mean(pull(problem1_df,vec_factor))
```

The mean of numbers and logical vectors is possible, however we can't take the mean of characters or factors. 

### Subsection 3: Convert variable to numeric
```{r}
as.numeric(pull(problem1_df,vec_log))
as.numeric(pull(problem1_df,vec_char))
as.numeric(pull(problem1_df,vec_factor))
```

We are unable to convert a character into a numeric, however we are able to convert a logic and factor into numeric.
